Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)

### 2014-03-02 authorinstr_2.tex
Earthquake detection toegevoegd. Event alignment aangepast. Alles nog WIP

\section{Tweet stream analysis}
\subsection{Statistics}
\subsection{user modeling}
\subsection{Classification}
\subsection{Tag based analysis}
\subsection{Event identification}
\subsubsection{What is Event Identification}
Event identification is the problem of identifying events(e.g. concerts, festivals \& incidents) in a twitter-stream. The events identified range from Worldwide to local events. Twitter-messages related to an event can be a useful source of information as they often spread news earlier than the 'old' media (e.g News Papers \& News Sites)

@@

After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by \cite{eventident} to identify an event cluster. 
\begin{itemize}
  \item Temporal: TODO
  \item Social: The interactions between users(e.g. retweets, replies \& mentions) during events could differ from other activities. 
  \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
  \item Twitter-centric: TODO
\end{itemize}
With this list of features two event-classifiers are trained using two different techniques. The first classifier is trained using the "WEKA tookit"(TODO), in the second classifier the  Naive-Bayes technique is used. According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters. 
\\\\
\textbf{Aligning Tweets with an Event} \\
On average thousands of tweets are sent every minute using Twitter(bron) . One of the main challenges in Event Identification is the alignment of tweets with their respective event. \cite{eventalign} tries to create an automated mapping solution for this problem using semantics.  
Twitter exposes the data using different formats such as JSON \& XML. To make this data more machine readable \cite{eventalign} enrich the data with sematics, after this process the data can then  be used as linked data which is more machine readable. The full enrichment process is described in section 2 of \cite{eventalign}. 
TODO
\section{Conclusion}

>>>>

\section{Tweet stream analysis}
\subsection{Statistics}
\subsection{user modeling}
\subsection{Classification}
\subsection{Tag based analysis}
\subsection{Event identification}

Event identification is the problem of identifying events(e.g. concerts, festivals \& incidents) in a twitter-stream. The events identified range from Worldwide to local events. Twitter-messages related to an event can be a useful source of information as they often spread news earlier than the 'old' media (e.g News Papers \& News Sites)

@@

After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by \cite{eventident} to identify an event cluster. 
\begin{itemize}
	%TODO Temporal en Twittercentric uitwerken.
  \item Temporal:
  \item Social: The interactions between users(e.g. retweets, replies \& mentions) during events could differ from other activities. 
  \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
  \item Twitter-centric: 
\end{itemize}
%TODO Weka toolkit uitzoeken
With this list of features two event-classifiers are trained using two different techniques. The first classifier is trained using the "WEKA tookit", in the second classifier the  Naive-Bayes technique is used. According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters. 
\\\\
\textbf{Aligning Tweets with an Event} \\
On average thousands of tweets are sent every minute using Twitter(bron) . One of the main challenges in Event Identification is the alignment of tweets with their respective event. \cite{eventalign} tries to create an automated mapping solution for this problem using semantics.

At first the data is enriched, Twitter exposes the data using different formats such as JSON \& XML. To make this data more machine readable \cite{eventalign} enrich the data with sematics, after this process the data can then  be used as linked data which is more machine readable. The full enrichment process is described in section 2 of \cite{eventalign}.

%TODO misschien wat meer info over het semantic web toevoegen.
After this process \cite{eventalign} uses multiple techniques to align a tweet with the respective event. The first technique used by \cite{eventalign} is Feature Extraction. Three featuresets are used:
\begin{itemize}
%TODO uitwerken
  \item Immediate Resource Leaves: TODO
  \item 1-Step Resource Leaves 
  \item DBPedia Concepts 
\end{itemize}
%TODO afmaken

\subsubsection{Usecase: Earthquake Detection}
In \cite{earthq} a usecase for Event Identification is presented in the form of a earthquake detection system. \cite{earthq} considers twitter users as sensors. If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an earthquake is occurring.

To distinguish between tweets about Earthquakes a number of features is used. (1) The number of words in a tweet (2) The words in a tweet (3) Word context features. Feature (1) is a surprisingly good way to classify tweets about earthquakes, especially if it is used with a big amount of users.

With the above feature set as basis, a system that detects earthquakes using twitter was built. After the system detects an earthquake an email to all users is sent. The system was used during 18. august - 2 September. In this time period 10 earthquakes had occurred, all of these earthquakes were detected. Furthermore \cite{earthq}'s system detects an earthquake 10 minutes after happening and sends a message within a minute after detection. 
\section{Conclusion}
